Minimizing post-shock forecasting error using disparate information

### 2020-06-12 manuscript/manuscript.tex
Revisions to abstract, introduction, simulation, data analysis, and discussions.

\begin{enumerate}
  \item Proposition for uniqueness of $\mathbf{W}^*$ is added.
  \item Introduction is revised with additional references.
  \item Data analysis is revised by fixing previous coding error.
  \item Simulation description is updated.
  \item Discussion is revised according to comments.
\end{enumerate}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction. Bootstrap procedures are provided to estimate the variability of our shock effect estimators and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock. It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.  However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study. One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error.
%When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.

@@

Data integration for forecasting is a broad area of research including ideas from many areas. Time-series pooling methods are a popular data integration method for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.  However, the issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded.  \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.

@@

Up to the scale of the shock, it is very unlikely that the above mentioned  statistical models or machine learning methods will work ideally since they are trained on the time series data that do not experience such a shock. To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration. We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. The main idea is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, to the original forecast at the known shock time point.

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap. Our simulation results show that  bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020-03-09, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

@@

Note that $\mathbf{V}$ is $2p \times n$. Then, the following proposition details some conditions when $\mathbf{W}^*$ is unique.

@@

If the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$. However, when $2p < n$, $\mathbf{W}^*$ may not be unique.

Estimation properties of $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm IVW}$, 
and $\hat{\alpha}_{\rm wadj}$ are discussed in the remaining sections.

@@

In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement and the other without any resampling of the donor pool. We first illustrate the simple bootstrap without resampling the donor pool. The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool. initialize $y_{i,0}$ for all $i \in I$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
Once can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$. Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$. When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however, if the constraints used to obtain $\mathbf{W}^*$ are binding then our bootstrap procedure needs to be modified \citep{li2019statistical}. The subsampling method in Section 4 of \citet{li2019statistical} can be adapted to our post-shock setting when the constraints are binding.

Let 
$
  \overline{\hat{\alpha}_{\mrm{adj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because it is a linear combination of OLS estimates with random weights. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

We stress that the above approximation is conditioned on $\Theta$ and the donor pool, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$. %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population. For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$. 
For parametric bootstrap without conditioning on the donor pool but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold. Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.

@@

In this section, we provide justification for our methods based on simulation examples. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=13$ and $\mu_{\alpha}=10$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(10, 5)$ that are further rounded to integers. This process is repeated until $T_i > 2p + 3$ for all $i\in \{1, \ldots, n + 1\}$ to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. It is designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. Moreover, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

@@

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    Risk-reduction proposition & 1 & 1 & 1\\
    Risk reduction & 28.126 & 28.179 & 25.834
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}. The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator. Note that this parametric bootstrap procedure is conditioned  on the  donor pool. Table \ref{table2} tells that all three proposed  shock-effect estimators are usable in the sense that the forecast employing them is better than the one without; and the $\hat{\alpha}_{\rm wadj}$ is the best in terms of the estimated risk-reduction quantity. Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an MSE of 97.422 whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  MSE of 19.599,  19.647, and 19.484, respectively.
Therefore, results proposed by Table \ref{table2} are verified with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. However, the risk-reduction quantities are inconsistent with the reality. The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.

We also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.962$, $2.812$, and $1.354$, respectively. These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect. There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding. Our apriori justification comes from \citet{kilian2009not} who study the effect that different supply and demand shocks have on oil prices through a vector auto regressive model. Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context. %This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.

However, from another perspective, this phenomenon can be explained by the fact that the donor pool is not constructed to be similar enough to the time series of interest. The shock(s) on March 9, 2020 in the midst of the COVID-19 pandemic and oil production volatility. It is difficult to find available stock market time series data that were generated under a similar setting.

@@

For the use of our methodology, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest. We recommend using parametric bootstrap without conditioning on the donor pool when the donor pool size $n$ is large, and the one conditioned on the donor pool when $n$ is small.

>>>>

\begin{enumerate}
  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
\end{enumerate}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction. Bootstrap procedures are provided to estimate the variability of our shock effect estimators and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. The risk-reduction conditions are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock. It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.  However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study. One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error. Then, we discuss some frequently used methodologies that may be applied in this situation.
%When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.

@@

As alternatives to forecast combination, data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas. Time-series pooling methods are frequently used for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.  Recent researches in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction, whose ideas are similar to ours. For instance, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
  \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.

@@

Up to the scale of the shock, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock. To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration. We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. The main idea is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, to the original forecast at the known shock time point.

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap. These propositions are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well, using estimates from bootstrap procedures. Our simulation results show that the proposed bootstrap estimation and the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

@@

@@

Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.  Note that $\mathbf{V}$ is $2p \times n$. Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$. However, when $2p < n$, $\mathbf{W}^*$ may not be unique.

@@

In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, and checks the underlying conditions of our risk reduction results in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement and the other without any resampling of the donor pool. We denote them by $\mc{B}_1$ and  $\mc{B}_2$, respectively. We first illustrate the simple $\mc{B}_2$. The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool. Initialize $y_{i,0}$ for all $i \in I$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
One can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

$\mc{B}_1$ is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^{(b)}$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^{(b)}$. Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$.

%When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however,

$\mc{B}_1$ takes the perspective of treating the donor-pool candidates to be random while $\mc{B}_2$ takes them as fixed. Therefore, it is possible that $\mc{B}_1$ can improve precision of $\mc{B}_2$.  Notice that $\mathbf{W}^*$ is random in $\mc{B}_1$. It is likely that  $\mc{B}_1$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ since $\mathbf{W}^*$ may possibly take values on the boundary of the parameter space \citep{andrews2000inconsistency}. For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$. The subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$ and $m/n \to 0$ as $n \to \infty$. However, we may leave its mathematical justification for future research. Note that this problem will not occur under  $\mc{B}_2$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$.

Let 
$
  \overline{\hat{\alpha}_{\mrm{adj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_i^{(b)}
$, 
$
  \overline{\hat{\alpha}_{\mrm{wadj}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
$, 
and 
$
  \overline{\hat{\alpha}_{\mrm{IVW}}} 
    = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}\hat{\alpha}_{{\rm IVW}, i}^{(b)}.
$
The almost-sure convergence results for $\hat{\alpha}_{\mrm{adj}}$ and $\hat{\alpha}_{\mrm{wadj}}$ follow naturally, provided that the regularity conditions outlined in \citet{bose1988edgeworth} hold. The proof for the case of $\overline{\hat{\alpha}_{\mrm{wadj}}}$, the sample mean of the bootstrapped weighted adjustment estimator, can be presented as below. As $B \to \infty$,
\begin{align*}
  \overline{\hat{\alpha}_{\mrm{wadj}}}
  = \frac{1}{B} \sum_{b=1}^B \sum_{i=2}^{n+1}w_i^* \hat{\alpha}_i^{(b)}
  = \sum_{i=2}^{n+1}w_i^* \frac{1}{B} \sum_{b=1}^B\hat{\alpha}_i^{(b)}
  \overset{a.s.}{\rightarrow} \sum_{i=2}^{n+1}w_i^* \alpha_i 
  =\E{\hat{\alpha}_{\rm wadj}|\Theta}.
\end{align*}
The case for the sample variance of the bootstrapped weighted adjustment estimator is similar. The same rationale holds for the adjustment estimator as well since it is a linear combination of OLS estimates, and the weights are not random conditioned on $\Theta$. However, the case for $\hat{\alpha}_{\rm IVW}$ is slightly different because its weights are random. It is not clear with respect to whether similar consistency results holds for $\hat{\alpha}_{\rm IVW}$. We would only claim that our bootstrap procedure provides an approximation for the case of $\hat{\alpha}_{\rm IVW}$.

@@

We stress that the above approximation is conditioned on $\Theta$ and for $\mc{B}_2$, and that bootstrapping cannot alleviate the inherent bias of using our adjustment estimators as estimates for $\alpha_1$. %Under a random-effect structure, every true shock effect of a time series in reality isan observed value from a population. For example, $\overline{\hat{\alpha}_{\rm wadj}}\overset{a.s.}{\rightarrow}\E{\hat{\alpha}_{\rm wadj}|\Theta}$ and $\overline{\hat{\alpha}_{\rm wadj}} \not\overset{a.s.}{\rightarrow}\E{\alpha_1}$ but $\E{\E{\hat{\alpha}_{\rm wadj}|\Theta}}=\E{\alpha_1}$. 
For $\mc{B}_1$ but conditioned on $\Theta$, we stress that the $\mathbf{W}^*$ from SCM method will become random, and that the consistency results may not hold. Simulation for justification of the parametric bootstrap is provided in Section \ref{parametricbootstrapsimulation}.

@@

In this section, we provide justification for our methods based on Monte Carlo simulation examples. We implemented our simulation based on $\mc{M}_{22}$ with negligibly small $\Sigma_{\gamma}$ and $\Sigma_{\delta}$ approximating the design of $\mathcal{M}_{21}$.  We consider $p=13$ and $\mu_{\alpha}=10$, where $p = 13$ is set to satisfy conditions in Proposition \ref{uniqueness}.

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers. If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.  It is set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$. In that case, we do not consider such $b$ in computations of means and variances. Additionally, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

@@

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

Using the parametric bootstrap proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}. Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $28.031$, $28.084$, and $25.748$, respectively. The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator. Note that this parametric bootstrap procedure is conditioned  on the  donor pool. Then, we verify the consistency of the result yielded by risk-reduction propositions with the reality as below.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an RMSE of 19.680 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.436$, $4.441$, and $4.423$ dollars, respectively.
Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. However, the risk-reduction quantities are inconsistent with the reality. The empirical MSE votes for $\hat{\alpha}_{\text{IVW}}$ though the estimates of  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ are fairly close shown by Figure~\ref{Fig:CP}.

The phenomenon that the true shock effect is not recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ can be due to that the donor pool is not constructed to be similar enough to the time series of interest. The shock(s) on March 9, 2020 is(are) in the midst of the COVID-19 pandemic and oil production volatility. It is difficult to find available stock market time series data that were generated under a similar setting.

From another perspective, it is possible that the stock of Conoco Phillips actually experienced multiple shocks on 2020 March 9th. For example, \citet{kilian2009not} studied the effect that different supply and demand shocks have on oil prices through a vector auto regressive model. Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context. Motivated by his study, we also studied additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27, 2014 shock effect; and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  RMSEs of $1.382$, $1.657$, and $1.145$ dollars, respectively. These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect. 
%There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding.  %This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.

@@

For the use of our methodology, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest. We recommend using $\mc{B}_1$ when the donor pool size $n$ is large, and $\mc{B}_2$ when $n$ is small.
